%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ayan Ginet} % Your name
\address{Kabanbay Batyr Avenue 53, Nur-Sultan (Astana), Kazakhstan 010000} % Your address
\address{ \faEnvelopeO~ayan.ginet@gmail.com \faGithub~github.com/ayanginet \faLinkedin~linkedin.com/in/ayanginet} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%    EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Nazarbayev University, Kazakhstan} \hfill {\em Aug 2017 - Jun 2021} \\ 
B.S. in Computer Science 
\end{rSection}

%----------------------------------------------------------------------------------------
%    WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\textbf{Note:} I also received an offer for \textbf{Software Engineering Intern} position at \textbf{Facebook London} for Summer 2020. However, the internship got canceled due to \textbf{COVID-19}.
\smallskip

\begin{rSubsection}{Ethereum Foundation}{ Jun 2020 - Present}{Software Engineering Intern}{Remote}
\item Developed transparent, decentralized web applications using Solidity, Web3.js, React.js.
\item Currently working on the storage system that makes a hash of event signatures human-readable.
\item \textbf{Tech Stack:} Python, Solidity, Web3.js, Ganache, Truffle, React, Django, Git.
\end{rSubsection}

\begin{rSubsection}{Nazarbayev University}{ May 2020 - Aug 2020}{Software Engineering Intern}{Remote}
\item Worked full-stack on the development of an open collaboration project for the historical sites in Kazakhstan.
\item Reduced the response time \textbf{from 5.6 seconds to 0.8 seconds} by applying request optimization on database queries.
\item Dockerized the Django project and deployed it on AWS instance.
\item \textbf{Tech Stack:} Python, JavaScript, Django, PostgreSQL, Docker, AWS.
\end{rSubsection}

\begin{rSubsection}{Google}{ Jul 2019 - Sep 2019}{Summer Trainee Engineering Program (STEP) Intern}{Zurich, Switzerland}

\item Expanded the set of contextual sources for Next Generation Assistant (NGA) by implementing conversational queries in Google Photos.
\item Measured latency and verified that new feature is under a given time limit.
\item Fixed several bugs related to the new feature and added support for internal debugging tools.
\item \textbf{Tech Stack:} C++, Python, Java, Bash, Mercurial.
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------
%    Personal Projects
%-------------------------------------------------------------

\begin{rSection}{Personal Projects}

\begin{rSubsection} {aika | ChatBot}{\em Jun 2018 - Nov 2018}{https://github.com/ayanginet/aika}

\item Developed chatbot that understands the message intent using the Bag of Words algorithm.
\item Integrated with Yandex Speech-To-Text API to make the bot more interactive.
\item Improved UX by decreasing response time \textbf{from 8 seconds, to 1.5 seconds} by caching.
\item \textbf{Tech Stack:} Python, nltk, sklearn, Yandex Speech API, Telegram Bot API, Heroku.
\end{rSubsection}
Other projects are available at github.com/ayanginet/
\end{rSection}

%-------------------------------------------------------------
%    Achievments
%----------------------------------------------------------------------------------------


\begin{rSection}{Achievements}

\begin{rCuteList}
%\item Completed 10 week long Facebook's Above\&Beyond Computer Science program. 
\item As a team, we scored \textbf{top 3\% percentile} at Google HashCode Qualification Round 2020.
\item \textbf{2nd place out of 15} teams at Astana Innovation Challenge 2018 (Hackathon).
\item Won \textbf{3rd place out of 40} teams at hackathon organized by \textbf{Unicef} with \textbf{IoT project for pharmacies.}
\item \textbf{3rd place} in Method Pro Hackathon, Sentiment Analysis for texts in Russian with \textbf{72\% accuracy rate}. 
\end{rCuteList}


\end{rSection}


%----------------------------------------------------------------------------------------
%    TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Programming Languages & C++, Python, JavaScript\\
%Databases & PostgreSQL, MySQL, Google Firebase \\
%Other Tools & Django, Git, Mercurial
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%    EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
